Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2021-12-13 reports/manuscript.Rmd
Add age moderation into manuscript and plots

Today, the same arguments that were once leveled against reading, schooling, and radio are being made about screen time (e.g., TV or computers) [@wartellaChildrenComputersNew2000]. Excessive screen time is the number one concern parents have about their children's health and behaviour, ahead of nutrition, bullying, and physical inactivity [@rhodes2015top]. Yet, the evidence to support parents' concerns is lacking. A 2019 Lancet editorial [@thelancetSocialMediaScreen2019a] suggested that , "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."

While some forms of screen time (e.g., TV viewing) may be detrimental to behaviour and health [@haleScreenTimeSleep2015a;@sweetserActivePassiveScreen2012a], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004a;@warburton2017children]. Thus, efforts to determine the effect of screen exposure on youth is "a defining challenge of the digital age" [@orbenAssociationAdolescentWellbeing2019]. With concerns over the impact of screen time including education, health, and psychological well-being, a broad overview that acknowledges screen time's potential benefits and risks is needed.

>>>>

Today, the same arguments that were once leveled against reading, schooling, and radio are being made about screen time (e.g., TV or computers) [@wartellaChildrenComputersNew2000]. Excessive screen time is the number one concern parents have about their children's health and behaviour, ahead of nutrition, bullying, and physical inactivity [@rhodes2015top]. Yet, the evidence to support parents' concerns is lacking. A 2019 Lancet editorial [@thelancetSocialMediaScreen2019] suggested that , "Our understanding of the benefits, harms, and risks of our rapidly changing digital landscape is sorely lacking."

While some forms of screen time (e.g., TV viewing) may be detrimental to behaviour and health [@haleScreenTimeSleep2015;@sweetserActivePassiveScreen2012], evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom) remains less certain and, in some cases, may even be beneficial [@liEarlyChildhoodComputer2004;@warburton2017children]. Thus, efforts to determine the effect of screen exposure on youth is "a defining challenge of the digital age" [@orbenAssociationAdolescentWellbeing2019]. With concerns over the impact of screen time including education, health, and psychological well-being, a broad overview that acknowledges screen time's potential benefits and risks is needed.
